\datedsubsection{ Nov. 2022 -- Dec. 2024 }
	{%
		Institut national d'histoire de l'art, \textit{Richelieu. Histoire du quartier}}
	{%
		\textbf{Research engineer}~}
	{%
		As the research engineer for the \textit{Richelieu. Histoire du quartier} programme, I have been in charge of conceiving and implementing a complete data processing pipeline: full-stack development of a web platform aimed towards researchers (REST API, data visualisation and mapping), PostgreSQL database modelling and administration, data migration, GIS management.}
\datedsubsection{ April 2022 -- Sept. 2022 }
	{%
		École normale supérieure, \textit{MSS/Katabase}}
	{%
		\textbf{End of studies internship}~ École nationale des Chartes}
	{%
		For the \textit{MSS/Katabase} research project, I worked towards automating the management and analysis of a database of 500 XML-TEI documents: text mining, named entity resolution and quantitative analysis. I redesigned of the project's \href{https://katabase.huma-num.fr/}{website} and established a REST API.}
\datedsubsection{ June 2021 -- Sept. 2021 }
	{%
		Archives nationales, \textit{ANR DesignSHS}}
	{%
		\textbf{Internship}~}
	{%
		From the inception of the \textit{DesignSHS} programme (funded by the French National Research Agency, or ANR), I participated in modelling and enriching a database of historical documents, before carrying out an exploratory study in data visualisation and statistical analysis.}
\datedsubsection{ March 2021 -- May 2021 }
	{%
		INA GRM}
	{%
		\textbf{End of studies internship}~École du Louvre}
	{%
		Within the National Audiovisual Institute's Music Reseach Group (INA GRM), I established a database of the GRM's academic publications: archival research, analysis of bibliographic metadata standards, comparative study of open-source database management systems.}
